%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Writing}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%  \cventry
%    {Founder \& Writer} % Role
%    {A Guide for Developers in Start-up} % Title
%    {Facebook Page} % Location
%    {Jan. 2015 - PRESENT} % Date(s)
%    {
%      \begin{cvitems} % Description(s)
%        \item {Drafted daily news for developers in Korea about IT technologies, issues about start-up.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
%  \cventry
%    {Undergraduate Student Reporter} % Role
%    {AhnLab} % Title
%    {S.Korea} % Location
%    {Oct. 2012 - Jul. 2013} % Date(s)
%    {
%      \begin{cvitems} % Description(s)
%        \item {Drafted reports about IT trends and Security issues on AhnLab Company magazine.}
%      \end{cvitems}
%    }
%ADD THIS TO YOUR CV
% Laboratory X-Ray-Assisted Device Alteration for Fault Isolation and Post-Silicon Debug
% Failure Analysis of Advanced Semiconductor Devices
 \cventrywrite
 {Celio, K. C., Sen, S., Nisenboim, E., Pardy, P. M., Nguyen, B., Le, V., \underline{Nolting, W.}, Kumar, S., Peterson, C. A., Raveh, A., Johnson, K., Stripe, B., Su, F., Lun, M., Lewis, S., Spink, R. I. and Yun, W.} % Role
  {Laboratory X-Ray-Assisted Device Alteration for Fault Isolation and Post-Silicon Debug} % Title
  {2024 IEEE International Reliability Physics Symposium (IRPS)} % Location
  {2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {To explore the utility of x-rays for LADA-like work, we have developed a first-of-a-kind x-ray-assisted device alteration (XADA) tool, with an industry-leading spot size and flux density, capable of interfacing with modern integrated circuit test equipment. We demonstrate for the first time the use of XADA for real fault isolation and post-silicon debug cases.}
      \end{cvitems}
    }
    \vspace{2.0mm}
%---------------------------------------------------------
\cventrywrite
{\underline{W. Nolting}, C. Durcan, S. Gassner, J. Goldberg, R. Balsano, Vincent P. Labella} % Role
{Nansocale Schottky Barrier Visualization Utilizing Computational Modeling and Ballistic Electron Emission Microscopy} % Title
{J. Appl. Phys} % Location
{2018} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item { The findings demonstrate the ability to detect the effects of partial silicide formation in the W and Cr samples and the presence of two barrier heights in intermixed Au/Ag films upon the electrostatic barrier of a buried interface with nanoscale resolution.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{L. Walsh, A. Green, A. Dou, \underline{W. Nolting}, et. al.} % Role
{Fermi Level Manipulation through Native Doping in the Topological Insulator Bi$_2$Se$_3$} % Title
{ACS Nano} % Location
{2018} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {We report the growth of near-intrinsic Bi2Se3 with a minimal Se vacancy concentration providing a Fermi level near midgap with no extrinsic counter-doping required. We also demonstrate the crucial ability to tuneEF from below midgap into the upper half of the gap near the conduction band edge by controlling the Se vacancy concentration using post-growth anneals.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{\underline{W. Nolting}, C. Durcan, V. P. Labella} % Role
{Detection of Silicide Formation in Nanoscale Visualization of Interface Electrostatics} % Title
{APL} % Location
{2017} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {The ability to detect localized silicide formation at a buried metal semiconductor Schottky interface is demonstrated via nanoscale measurements of the electrostatic barrier.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{\underline{W. Nolting}, C. Durcan, A. J. Narasimham, V. P. Labella} % Role
{Nanoscale Schottky Barrier Mapping of Thermally Evaporated and Sputter Deposited W/Si(001) Diodes Using Ballistic Electron Emission Microscopy} % Title
{JVST B} % Location
{2016} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Ballistic electron emission microscopy has been utilized to demonstrate differences in the interface electrostatics of tungsten-Si(001) Schottky diodes fabricated using two different deposition techniques: thermal evaporation using electron-beam heating and magnetron sputtering}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{B.T. McGowan, \underline{W. M. Nolting}, J.R. Lloyd} % Role
{Effects of Electrical Bias and Temperature Stress on the Negative Magnetoresistance of a Low-k Dielectric} % Title
{J. Appl. Phys} % Location
{2015} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {A study of the effect of electrical bias and temperature stress (BTS) on the negative magnetoresistance (MR) of a low-k dielectric composed of SiCOH is presented.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{D.K. Misra, S. Sumithra, N.S. Chauhan. \underline{W. M. Nolting}, P.F.P. Poudeu, Kevin L. Stokes} % Role
{Correlation Between Microstructure and Drastically Reduced Lattice Thermal Conductivity in Bi$_2$Te$_3$/Bi Nanocomposites for High Thermoelectric Figure of Merit} % Title
{Mater. Sci. in Semiconductor Processing} % Location
{2015} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {D.K. Misra, S. Sumithra, N.S. Chauhan. W. M. Nolting, P.F.P. Poudeu, Kevin L. Stokes}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{S. Sumithra, N. J. Takas, \underline{W. M. Nolting}, S. Sapkota, P.F.P. Poudeu, and K.L. Stokes} % Role
{Effect of NiTe Nanoinclusions on Thermoelectric Properties of Bi$_2$Te$_3$} % Title
{Journal of Electronic Materials} % Location
{2012} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {S. Sumithra, N. J. Takas, W. M. Nolting, S. Sapkota, P.F.P. Poudeu, and K.L. Stokes}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{S. Sumithra, N. J. Takas, D. K. Misra, \underline{W. M. Nolting}, P. F. P. Poudeu, and K. L. Stokes} % Role
{Enhancement in Thermoelectric Figure of Merit in Nanostructured Bi$_2$Te$_3$ with Semimetal Nanoinclusions} % Title
{Adv. Energy Materials} % Location
{2011} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {S. Sumithra, N. J. Takas, D. K. Misra, W. M. Nolting, P. F. P. Poudeu, and K. L. Stokes}
  \end{cvitems}
}

%---------------------------------------------------------
\cventrywrite
{\underline{W. Nolting}, K. L. Stokes} % Role
{Electronic Transport in Thermoelectric Bismuth Telluride} % Title
{University of New Orleans} % Location
{Scholar Works UNO Thesis Publication} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {W. Nolting, K. L. Stokes}
  \end{cvitems}
}

\end{cventries}
